---
title: "ADJACENT STATES ARIMAX MODEL"
output:
  pdf_document: default
  html_document: default
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
!!!!!!!!!!!!!!!!!!!
LOADING THE DATASET
!!!!!!!!!!!!!!!!!!!
```{r load-packages, echo=TRUE, results='hide', message=FALSE}
library("tidyr")
library("feasts")
library("MMWRweek")
library("data.table")
library("caret")
library("purrr")
library("skimr")
library("ggcorrplot")
library("DataExplorer")
#library("cdcfluview")
library("dplyr")
library("tseries")
library("forecast")
library("tsibble")
library("berryFunctions")
library("scoringutils")
library("covidHubUtils")
library("gtools")
library("parallel")
library("doParallel")
library("foreach")
library("future")#https://cran.r-project.org/web/packages/future/vignettes/future-4-issues.html
library("listenv")
library("lubridate")
library("corrplot")
library("sf")
library("ggrepel")
library("Metrics")
library("epitools")
```
!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
LOADING DATASET AND FUNCTION 
!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
```{r, echo=TRUE, message=FALSE}
###########################################
#       LOADING AND CLEANING THE DATASET  #        
###########################################

# Loads the ADJACENT states models
source("ES_ADJACENT.R", local = TRUE, chdir = TRUE)

# Loads the ILI dataset
my_data = read.csv("ILINet.csv")

# Loads the states names and codes
state_codes<-read.csv("State_Codes.csv")

#Combines the ILI data into separate lists each one with its state name and removes the states that are not in the contiguous U.S.
list_of_states<-combining_states_data(my_data,state_codes) %>% 
  setNames(state_codes$location_name)%>%                    
  .[c(-48,-49,-50,-51,-52,-53)]                             
                                                            
```
Function Description

```{r, include=FALSE}
##############################################################################
# AUTO ARIMAX ADJACENT STATES model
# With the mclapply we use a list of states and read one at the time
# We have an auto arimax, and ensembles of 27 and 64 models
# You can set: auto =TRUE or ES27=TRUE or ES64=TRUE to chose one of them
# my_n_ahead is the number of weeks ahead you want to forecast
# in this case states_data is needed for calculating mean cases by each state
# mc.cores is the number of cores you want to use to run the model

```

EXAMPLE FOR A SINGLE STATE

```{r, include=FALSE}
# A list with a single state from the states_data
source("ES_ADJACENT.R", local = TRUE, chdir = TRUE)

one_state<-list(list_of_states[['Alabama']])

AUTO_example <- mclapply(one_state, ES_ADJACENT, auto=TRUE, n_weeks_ahead=1,list_of_states=list_of_states, week_lag=1, mc.cores=1)

ES27_example <- mclapply(one_state, ES_ADJACENT, ES27=TRUE, n_weeks_ahead=1,list_of_states=list_of_states, week_lag=1, mc.cores=1)

ES64_example <- mclapply(one_state, ES_ADJACENT, ES64=TRUE, n_weeks_ahead=1,list_of_states=list_of_states, week_lag=1, mc.cores=1)

```

AUTO ADJACENT WEEK1 - ALL STATES

```{r}

AUTO_ADJACENT_WEEK1_list <- mclapply(list_of_states, ES_ADJACENT, auto=TRUE, n_weeks_ahead=1,list_of_states=list_of_states,week_lag=1, mc.cores=4)%>%
  setNames(names(list_of_states))

# FINAL DATAFRAME
AUTO_ADJACENT_WEEK1 <- bind_rows(AUTO_ADJACENT_WEEK1_list, .id = "State")

```

AUTO ADJACENT WEEK2 - ALL STATES

```{r}
# RUN MODEL 
AUTO_ADJACENT_WEEK2_list <- mclapply(list_of_states, ES_ADJACENT, auto=TRUE, n_weeks_ahead=2,list_of_states=list_of_states,week_lag=1, mc.cores=4)%>%
  setNames(names(list_of_states))

# FINAL DATAFRAME
AUTO_ADJACENT_WEEK2 <- bind_rows(AUTO_ADJACENT_WEEK2_list, .id = "State")
```

AUTO ADJACENT WEEK3 - ALL STATES

```{r}

AUTO_ADJACENT_WEEK3_list <- mclapply(list_of_states, ES_ADJACENT, auto=TRUE, n_weeks_ahead=3,list_of_states=list_of_states,week_lag=1, mc.cores=4)%>%
  setNames(names(list_of_states))

# Combine the list of data frames into a single data frame with names as a column
AUTO_ADJACENT_WEEK3 <- bind_rows(AUTO_ADJACENT_WEEK3_list, .id = "State")
```

AUTO ADJACENT WEEK4 - ALL STATES

```{r}

AUTO_ADJACENT_WEEK4_list <- mclapply(list_of_states, ES_ADJACENT, auto=TRUE, n_weeks_ahead=4,list_of_states=list_of_states,week_lag=1, mc.cores=4)%>%
  setNames(names(list_of_states))

# Combine the list of data frames into a single data frame with names as a column
AUTO_ADJACENT_WEEK4 <- bind_rows(AUTO_ADJACENT_WEEK4_list, .id = "State")
```

```{r}
save.image("ADJACENT_MODELS_correct.Rdata")
```

ES27 ADJACENT WEEK1 - ALL STATES

```{r}

ES27_ADJACENT_WEEK1_list <- mclapply(list_of_states, ES_ADJACENT, ES27=TRUE, n_weeks_ahead=1,list_of_states=list_of_states,week_lag=1, mc.cores=4)%>%
  setNames(names(list_of_states))

# FINAL DATAFRAME
ES27_ADJACENT_WEEK1 <- bind_rows(ES27_ADJACENT_WEEK1_list, .id = "State")
```

ES27 ADJACENT WEEK2 - ALL STATES

```{r}

ES27_ADJACENT_WEEK2_list <- mclapply(list_of_states, ES_ADJACENT, ES27=TRUE, n_weeks_ahead=2,list_of_states=list_of_states,week_lag=1, mc.cores=4)%>%
  setNames(names(list_of_states))

# FINAL DATAFRAME
ES27_ADJACENT_WEEK2 <- bind_rows(ES27_ADJACENT_WEEK2_list, .id = "State")
```

ES27 ADJACENT WEEK3 - ALL STATES

```{r}

ES27_ADJACENT_WEEK3_list <- mclapply(list_of_states, ES_ADJACENT, ES27=TRUE, n_weeks_ahead=3,list_of_states=list_of_states,week_lag=1, mc.cores=4)%>%
  setNames(names(list_of_states))

# FINAL DATAFRAME
ES27_ADJACENT_WEEK3 <- bind_rows(ES27_ADJACENT_WEEK3_list, .id = "State")
```

ES27 ADJACENT WEEK4 - ALL STATES

```{r}

ES27_ADJACENT_WEEK4_list <- mclapply(list_of_states, ES_ADJACENT, ES27=TRUE, n_weeks_ahead=4,list_of_states=list_of_states,week_lag=1, mc.cores=4)%>%
  setNames(names(list_of_states))

# FINAL DATAFRAME
ES27_ADJACENT_WEEK4 <- bind_rows(ES27_ADJACENT_WEEK4_list, .id = "State")
```

```{r}
save.image("ADJACENT_MODELS_correct.Rdata")
```

ES64 ADJACENT WEEK1 - ALL STATES

```{r}

ES64_ADJACENT_WEEK1_list <- mclapply(list_of_states, ES_ADJACENT, ES64=TRUE, n_weeks_ahead=1,list_of_states=list_of_states, mc.cores=4)%>%
  setNames(names(list_of_states))

# FINAL DATAFRAME
ES64_ADJACENT_WEEK1 <- bind_rows(ES64_ADJACENT_WEEK1_list, .id = "State")
```

ES64 ADJACENT WEEK2 - ALL STATES

```{r}

ES64_ADJACENT_WEEK2_list <- mclapply(list_of_states, ES_ADJACENT, ES64=TRUE, n_weeks_ahead=2,list_of_states=list_of_states, mc.cores=4)%>%
  setNames(names(list_of_states))

# Combine the list of data frames into a single data frame with names as a column
ES64_ADJACENT_WEEK2 <- bind_rows(ES64_ADJACENT_WEEK2_list, .id = "State")

```

ES64 ADJACENT WEEK3 - ALL STATES

```{r}

ES64_ADJACENT_WEEK3_list <- mclapply(list_of_states, ES_ADJACENT, ES64=TRUE, n_weeks_ahead=3,list_of_states=list_of_states, mc.cores=4)%>%
  setNames(names(list_of_states))

# Combine the list of data frames into a single data frame with names as a column
ES64_ADJACENT_WEEK3 <- bind_rows(ES64_ADJACENT_WEEK3_list, .id = "State")

```

ES64 ADJACENT WEEK4 - ALL STATES

```{r}

ES64_ADJACENT_WEEK4_list <- mclapply(list_of_states, ES_ADJACENT, ES64=TRUE, n_weeks_ahead=4,list_of_states=list_of_states, mc.cores=4)%>%
  setNames(names(list_of_states))

# Combine the list of data frames into a single data frame with names as a column
ES64_ADJACENT_WEEK4 <- bind_rows(ES64_ADJACENT_WEEK4_list, .id = "State")

```

```{r}
save.image("ADJACENT_MODELS_correct.Rdata")
```
